Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-15 paper/paper.tex
More things

\begin{abstract}
    We discuss our experiences adapting three recent algorithms for maximum common (connected)
    subgraph problems to exploit multi-core parallelism. These algorithms are heavily irregular and
    very sensitive to search order changes, and so do not easily lend themselves to parallel search.
    Nonetheless, our results show that each algorithm can be parallelised successfully, with the
    threaded algorithms we create being clearly better than the sequential ones. We then look in
    more detail at the results, and discuss speedups should be measured for this kind of algorithm.
    Because of the difficulty in quantifying an average speedup when so-called anomalous
    speedups (superlinear and sublinear) are common, we propose a new measure called \emph{aggregate
    speedup}.
\end{abstract}

@@

        \begin{scope}[xshift=12cm]
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

We perform our experiments on systems with dual Intel Xeon E5-2640 v2 processors and 64GBytes RAM,
running Ubuntu 14.04, with GCC 5.3.0 as the compiler. Each machine has a total of sixteen cores, and
hyper-threading is enabled, so we run experiments with 32 threads except where otherwise noted, but
we do not expect speedups of 32 even in the best case.  We run all our experiments with a one
hundred second timeout for each instance. All of our sequential runtimes are from optimised
implementations which were not designed with parallelism in mind---that is, speedups from
parallelism are genuine improvements over the state of the art.

>>>>

\begin{abstract}
    We discuss our experiences adapting three recent algorithms for maximum common (connected)
    subgraph problems to exploit multi-core parallelism. These algorithms are heavily irregular and
    very sensitive to search order changes, and so do not easily lend themselves to parallel search.
    Nonetheless, our results show that each algorithm can be parallelised successfully, with the
    threaded algorithms we create being clearly better than the sequential ones. We then look in
    more detail at the results, and discuss how speedups should be measured for this kind of algorithm.
    Because of the difficulty in quantifying an average speedup when so-called anomalous
    speedups (superlinear and sublinear) are common, we propose a new measure called \emph{aggregate
    speedup}.
\end{abstract}

@@

        \begin{scope}[xshift=12cm]
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M7) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M8) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

We perform our experiments on systems with dual Intel Xeon E5-2640 v2 processors and 64GBytes RAM,
running Ubuntu 14.04, with GCC 5.3.0 as the compiler. Each machine has a total of sixteen cores, and
hyper-threading is enabled, so we run experiments with 32 threads except where otherwise noted, but
we do not expect speedups of 32 even in the ideal case.  We run all our experiments with a one
hundred second timeout for each instance. All of our sequential runtimes are from optimised
implementations which were not designed with parallelism in mind---that is, speedups from
parallelism are genuine improvements over the state of the art.
